
\section{Conclusion}
\label{sec:conclusion}

% summay of your proposed solution and findings  
In this paper, we have investigated the feasibility of using wireless sensing for parking spot occupancy detection in a low-cost and non-intrusive manner by detecting multiple parking spots simultaneously. We proposed a system that leverages off-the-shelf Wi-Fi devices to collect Channel State Information (CSI) data and employs machine learning techniques for classification. Our experimental results demonstrate that the proposed system can achieve an overall classification accuracy of 56\% in detecting parking spot occupancy states. The results indicate that the system performs well in identifying the states where all parking spots are either empty or occupied, as well as when only one parking spot is occupied. However, the system struggles with cases where two parking spots have the same state and the third one is different, particularly when the middle parking spot is involved. The overall accuracy we achieved is lower than expected, which we attribute to the quality of the CSI data collected and the limited number of classes. We believe that further improvements can be made by optimizing the placement of the transmitter and receiver devices, as well as by experimenting with real vehicles instead of model vehicles. When compared to the existing systems, our system is significantly cheaper and easier to deploy. With the promising results we obtained, we believe that our system can be further improved and optimized for practical applications in parking management systems.